---
title: "Accuracy of gene expression measurements"
author: "Jackie Roger"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  html_document: default
  # pdf_document: default
  # fig_caption: yes
---

```{r setup, include = FALSE}

# setwd("/Users/jacquelynroger/Desktop/expression_accuracy/expression_accuracy_v2")

library(magrittr)
library(readr)
library(dplyr)
library(ggplot2)
library(plotly)
library(tidyr)
library(RColorBrewer)
library(knitr)
library(forcats)
library(jsonlite)

```

### Background

The purpose of this Rmd is to quantify the accuracy of outlier gene expression measurements.

### Set sample & umend depth

```{r echo = TRUE}

sample_id <- 'TH34_1447_S01'
umend_depth <- 57.3

```

### Set file names

```{r echo = TRUE}

outlier_info <- read_tsv(paste0('data/outlier_results_', sample_id), col_types = cols())
threshold_info <- fromJSON('data/3.json')

```

### Get up outlier genes & measurements

```{r echo = TRUE}

pc_outlier_rows <- which(outlier_info$pc_outlier == 'pc_up')
pd_outlier_rows <- which(outlier_info$pd_outlier == 'pd_up')

pc_summary <- data.frame(matrix(nrow = length(pc_outlier_rows), ncol = 12))
colnames(pc_summary) <- c('gene',
                          'measurement',
                          'outlier_threshold',
                          'accuracy_threshold',
                          'percent_accurate_mean',
                          'percent_accurate_min',
                          'percent_accurate_max',
                          'percent_accurate_S1',
                          'percent_accurate_S2',
                          'percent_accurate_S3',
                          'percent_accurate_S4',
                          'percent_accurate_S5')

pd_summary <- data.frame(matrix(nrow = length(pd_outlier_rows), ncol = 46))
colnames(pd_summary) <- c('gene',
                          'measurement',
                          'pd_up1',
                          'pd_up2',
                          'pd_up3',
                          'pd_up4',
                          'outlier_threshold1',
                          'outlier_threshold2',
                          'outlier_threshold3',
                          'outlier_threshold4',
                          'accuracy_threshold1',
                          'accuracy_threshold2',
                          'accuracy_threshold3',
                          'accuracy_threshold4',
                          'percent_accurate_mean1',
                          'percent_accurate_mean2',
                          'percent_accurate_mean3',
                          'percent_accurate_mean4',
                          'percent_accurate_min1',
                          'percent_accurate_min2',
                          'percent_accurate_min3',
                          'percent_accurate_min4',
                          'percent_accurate_max1',
                          'percent_accurate_max2',
                          'percent_accurate_max3',
                          'percent_accurate_max4',
                          'percent_accurate1_S1',
                          'percent_accurate1_S2',
                          'percent_accurate1_S3',
                          'percent_accurate1_S4',
                          'percent_accurate1_S5',
                          'percent_accurate2_S1',
                          'percent_accurate2_S2',
                          'percent_accurate2_S3',
                          'percent_accurate2_S4',
                          'percent_accurate2_S5',
                          'percent_accurate3_S1',
                          'percent_accurate3_S2',
                          'percent_accurate3_S3',
                          'percent_accurate3_S4',
                          'percent_accurate3_S5',
                          'percent_accurate4_S1',
                          'percent_accurate4_S2',
                          'percent_accurate4_S3',
                          'percent_accurate4_S4',
                          'percent_accurate4_S5')

for (i in 1:length(pc_outlier_rows)) {
  pc_summary$gene[i] <- outlier_info$Gene[pc_outlier_rows[i]]
  pc_summary$measurement[i] <- outlier_info$sample[pc_outlier_rows[i]]
}

for (i in 1:length(pd_outlier_rows)) {
  pd_summary$gene[i] <- outlier_info$Gene[pd_outlier_rows[i]]
  pd_summary$measurement[i] <- outlier_info$sample[pd_outlier_rows[i]]
}

pd_summary$pd_up1 <- FALSE
pd_summary$pd_up2 <- FALSE
pd_summary$pd_up3 <- FALSE
pd_summary$pd_up4 <- FALSE

```

### Calculate accuracy thresholds

```{r echo = TRUE}

# Get pc outlier thresholds & calculate pc accuracy threshold

for (i in 1:nrow(pc_summary)) {
  threshold <- threshold_info$pancan_thresholds$high[pc_summary$gene[i]]
  if (!is.null(threshold)) {
    pc_summary$outlier_threshold[i] <- threshold
    acc <- ((pc_summary$measurement[i] - as.numeric(threshold)) / pc_summary$measurement[i]) * 100
    pc_summary$accuracy_threshold[i] <- acc
  }
}

# Get pd outlier thresholds & calculate pd accuracy thresholds

for (i in 1:nrow(pd_summary)) {
  threshold1 <- threshold_info$nof1_disease_thresholds$high[pd_summary$gene[i]]
  threshold2 <- threshold_info$pandis_thresholds$high[pd_summary$gene[i]]
  threshold3 <- threshold_info$first_degree_thresholds$high[pd_summary$gene[i]]
  threshold4 <- threshold_info$first_and_second_degree_thresholds$high[pd_summary$gene[i]]
  if (!is.null(threshold1)) {
    pd_summary$outlier_threshold1[i] <- threshold1
    if (pd_summary$measurement[i] > threshold1) {
      acc <- ((pd_summary$measurement[i] - as.numeric(threshold1)) / pd_summary$measurement[i]) * 100
      pd_summary$accuracy_threshold1[i] <- acc
      pd_summary$pd_up1[i] = TRUE
    }
  }
  if (!is.null(threshold2)) {
    pd_summary$outlier_threshold2[i] <- threshold2
    if (pd_summary$measurement[i] > threshold2) {
      acc <- ((pd_summary$measurement[i] - as.numeric(threshold2)) / pd_summary$measurement[i]) * 100
      pd_summary$accuracy_threshold2[i] <- acc
      pd_summary$pd_up2[i] = TRUE
    }
  }
  if (!is.null(threshold3)) {
    pd_summary$outlier_threshold3[i] <- threshold3
    if (pd_summary$measurement[i] > threshold3) {
      acc <- ((pd_summary$measurement[i] - as.numeric(threshold3)) / pd_summary$measurement[i]) * 100
      pd_summary$accuracy_threshold3[i] <- acc
      pd_summary$pd_up3[i] = TRUE
    }
  }
  if (!is.null(threshold4)) {
    pd_summary$outlier_threshold4[i] <- threshold4
    if (pd_summary$measurement[i] > threshold4) {
      acc <- ((pd_summary$measurement[i] - as.numeric(threshold4)) / pd_summary$measurement[i]) * 100
      pd_summary$accuracy_threshold4[i] <- acc
      pd_summary$pd_up4[i] = TRUE
    }
  }
}

```

### Get distribution of accuracies at that threshold
##### Note: the code in this code block was adapted from code written by Dr. Holly Beale

```{r echo = TRUE}

run_slow_step <- FALSE

if (run_slow_step == TRUE) {
  # Load data & groom read counts
  expression_results_raw <- read_tsv("data/expression_log2tpm1.txt.gz", col_types = cols())
  read_counts_raw <- read_tsv("data/read_counts.txt", 
                              col_names = c("sample_id", "measurement", "read_count"))
  evenly_selected_subsamples <-
    read_tsv(paste0("data/evenly_selected_subsamples_with_binwidth_4.tsv"), col_types = cols())
  read_counts_anno <- read_counts_raw %>% 
    mutate(target_UMEND_count = as.numeric(gsub("^.*_est([0-9]*)M_.*$", "\\1", sample_id)),
           parent_id = gsub("_est.*$", "", sample_id)) %>%
    spread(measurement, read_count)
  read_counts <- left_join(read_counts_anno, evenly_selected_subsamples %>%
                             select(sample_id, bin_median), by = "sample_id")
  # Calculate per gene expression
  long_expression_results <- expression_results_raw %>% gather(sample_id, expression, -gene)
  long_expression_results_anno <- long_expression_results %>%
    dplyr::filter( sample_id %in% evenly_selected_subsamples$sample_id) %>%
    left_join(read_counts %>%
                select(sample_id, target_UMEND_count, parent_id, UMEND, bin_median),
              by = "sample_id")
  abundance_step_1 <- long_expression_results_anno %>% 
    group_by(parent_id, gene) %>%
    mutate(expression_at_max_depth = expression[target_UMEND_count == max(target_UMEND_count)],
           max_expression_of_gene = max(expression),
           f_expression_at_max_depth_Gt0 = expression_at_max_depth > 0) 
}

# Get pc accuracy distributions

for (i in 1:5) {
  # Set accuracy threshold and get accuracy info
  threshold_for_percent_of_total <- pc_summary$accuracy_threshold[i]
  abundance_step_2 <- abundance_step_1 %>%
    dplyr::filter(f_expression_at_max_depth_Gt0)  %>% 
    mutate(within_accuracy_threshold_of_deepest_val =
             expression > (1 - threshold_for_percent_of_total / 100) * expression_at_max_depth &
             expression < (1 + threshold_for_percent_of_total / 100) * expression_at_max_depth)
  non_zero_abundance <- abundance_step_2
  # Make expression bins and generate summary statistics
  break_sequence <- c(0, 1, 3, 5, 7, 10, 20, 30, 50, ceiling(max(non_zero_abundance$expression_at_max_depth)))
  set.seed(1)
  abundance_by_expression_bin <- non_zero_abundance %>% 
    ungroup() %>% 
  	mutate(expression_bin = cut(expression_at_max_depth, breaks = break_sequence, dig.lab = 6))
  abundance_stats <- abundance_by_expression_bin	%>% 
  	group_by(expression_bin, bin_median, UMEND, parent_id ) %>%
  	summarize(pct_accurately_measured = sum(within_accuracy_threshold_of_deepest_val) / n(),
  	          n_genes_in_bin = length(unique(gene)),
  	          expression_bin_label = paste0(gsub("]", "", gsub(",", "-", gsub("[\\(]*", "",
  	                                        unique(expression_bin)))), " (n=", n_genes_in_bin, ")")) 
  write_tsv(abundance_stats, paste0('data/expression_data/pc/abundance_by_expression_bin-pc', i, '.tsv'))
}

# Get pd accuracy distributions

for (i in 1:5) {
  # Threshold 1
  if(pd_summary$pd_up1[i] == TRUE) {
    # Set accuracy threshold and get accuracy info
    threshold_for_percent_of_total <- pd_summary$accuracy_threshold1[i]
    abundance_step_2 <- abundance_step_1 %>%
      dplyr::filter(f_expression_at_max_depth_Gt0)  %>% 
      mutate(within_accuracy_threshold_of_deepest_val =
               expression > (1 - threshold_for_percent_of_total / 100) * expression_at_max_depth &
               expression < (1 + threshold_for_percent_of_total / 100) * expression_at_max_depth)
    non_zero_abundance <- abundance_step_2
    # Make expression bins and generate summary statistics
    break_sequence <- c(0, 1, 3, 5, 7, 10, 20, 30, 50, ceiling(max(non_zero_abundance$expression_at_max_depth)))
    set.seed(1)
    abundance_by_expression_bin <- non_zero_abundance %>% 
      ungroup() %>% 
    	mutate(expression_bin = cut(expression_at_max_depth, breaks = break_sequence, dig.lab = 6))
    abundance_stats <- abundance_by_expression_bin	%>% 
    	group_by(expression_bin, bin_median, UMEND, parent_id ) %>%
    	summarize(pct_accurately_measured = sum(within_accuracy_threshold_of_deepest_val) / n(),
    	          n_genes_in_bin = length(unique(gene)),
    	          expression_bin_label = paste0(gsub("]", "", gsub(",", "-", gsub("[\\(]*", "",
    	                                        unique(expression_bin)))), " (n=", n_genes_in_bin, ")")) 
    write_tsv(abundance_stats, paste0('data/expression_data/pd/abundance_by_expression_bin-pd', i, '_1.tsv'))
  }
  # Threshold 2
  if(pd_summary$pd_up2[i] == TRUE) {
    # Set accuracy threshold and get accuracy info
    threshold_for_percent_of_total <- pd_summary$accuracy_threshold2[i]
    abundance_step_2 <- abundance_step_1 %>%
      dplyr::filter(f_expression_at_max_depth_Gt0)  %>% 
      mutate(within_accuracy_threshold_of_deepest_val =
               expression > (1 - threshold_for_percent_of_total / 100) * expression_at_max_depth &
               expression < (1 + threshold_for_percent_of_total / 100) * expression_at_max_depth)
    non_zero_abundance <- abundance_step_2
    # Make expression bins and generate summary statistics
    break_sequence <- c(0, 1, 3, 5, 7, 10, 20, 30, 50, ceiling(max(non_zero_abundance$expression_at_max_depth)))
    set.seed(1)
    abundance_by_expression_bin <- non_zero_abundance %>% 
      ungroup() %>% 
    	mutate(expression_bin = cut(expression_at_max_depth, breaks = break_sequence, dig.lab = 6))
    abundance_stats <- abundance_by_expression_bin	%>% 
    	group_by(expression_bin, bin_median, UMEND, parent_id ) %>%
    	summarize(pct_accurately_measured = sum(within_accuracy_threshold_of_deepest_val) / n(),
    	          n_genes_in_bin = length(unique(gene)),
    	          expression_bin_label = paste0(gsub("]", "", gsub(",", "-", gsub("[\\(]*", "",
    	                                        unique(expression_bin)))), " (n=", n_genes_in_bin, ")")) 
    write_tsv(abundance_stats, paste0('data/expression_data/pd/abundance_by_expression_bin-pd', i, '_2.tsv'))
  }
  # Threshold 3
  if(pd_summary$pd_up3[i] == TRUE) {
  # Set accuracy threshold and get accuracy info
    threshold_for_percent_of_total <- pd_summary$accuracy_threshold3[i]
    abundance_step_2 <- abundance_step_1 %>%
      dplyr::filter(f_expression_at_max_depth_Gt0)  %>% 
      mutate(within_accuracy_threshold_of_deepest_val =
               expression > (1 - threshold_for_percent_of_total / 100) * expression_at_max_depth &
               expression < (1 + threshold_for_percent_of_total / 100) * expression_at_max_depth)
    non_zero_abundance <- abundance_step_2
    # Make expression bins and generate summary statistics
    break_sequence <- c(0, 1, 3, 5, 7, 10, 20, 30, 50, ceiling(max(non_zero_abundance$expression_at_max_depth)))
    set.seed(1)
    abundance_by_expression_bin <- non_zero_abundance %>% 
      ungroup() %>% 
    	mutate(expression_bin = cut(expression_at_max_depth, breaks = break_sequence, dig.lab = 6))
    abundance_stats <- abundance_by_expression_bin	%>% 
    	group_by(expression_bin, bin_median, UMEND, parent_id ) %>%
    	summarize(pct_accurately_measured = sum(within_accuracy_threshold_of_deepest_val) / n(),
    	          n_genes_in_bin = length(unique(gene)),
    	          expression_bin_label = paste0(gsub("]", "", gsub(",", "-", gsub("[\\(]*", "",
    	                                        unique(expression_bin)))), " (n=", n_genes_in_bin, ")")) 
    write_tsv(abundance_stats, paste0('data/expression_data/pd/abundance_by_expression_bin-pd', i, '_3.tsv'))
  }
  # Threshold 4
  if(pd_summary$pd_up4[i] == TRUE) {
    # Set accuracy threshold and get accuracy info
    threshold_for_percent_of_total <- pd_summary$accuracy_threshold4[i]
    abundance_step_2 <- abundance_step_1 %>%
      dplyr::filter(f_expression_at_max_depth_Gt0)  %>% 
      mutate(within_accuracy_threshold_of_deepest_val =
               expression > (1 - threshold_for_percent_of_total / 100) * expression_at_max_depth &
               expression < (1 + threshold_for_percent_of_total / 100) * expression_at_max_depth)
    non_zero_abundance <- abundance_step_2
    # Make expression bins and generate summary statistics
    break_sequence <- c(0, 1, 3, 5, 7, 10, 20, 30, 50, ceiling(max(non_zero_abundance$expression_at_max_depth)))
    set.seed(1)
    abundance_by_expression_bin <- non_zero_abundance %>% 
      ungroup() %>% 
    	mutate(expression_bin = cut(expression_at_max_depth, breaks = break_sequence, dig.lab = 6))
    abundance_stats <- abundance_by_expression_bin	%>% 
    	group_by(expression_bin, bin_median, UMEND, parent_id ) %>%
    	summarize(pct_accurately_measured = sum(within_accuracy_threshold_of_deepest_val) / n(),
    	          n_genes_in_bin = length(unique(gene)),
    	          expression_bin_label = paste0(gsub("]", "", gsub(",", "-", gsub("[\\(]*", "",
    	                                        unique(expression_bin)))), " (n=", n_genes_in_bin, ")")) 
    write_tsv(abundance_stats, paste0('data/expression_data/pd/abundance_by_expression_bin-pd', i, '_4.tsv'))
  }
}

```

### Find probabilities that purported outliers are true outliers

```{r echo = TRUE}

umend_depth_bins_all <- seq(0, 44, 4)
expression_bins_all <- c('0-1', '1-3', '3-5', '5-7', '7-10', '10-15')

# Figure out umend depth bin

if (umend_depth >= 42) {
  umend_depth_bin <- 44
} else {
  for (i in 1:(length(umend_depth_bins_all) - 1)) {
    if (((umend_depth_bins_all[i] - umend_depth) <= 2) &&
        ((umend_depth - umend_depth_bins_all[i]) < 2)) {
      umend_depth_bin <- umend_depth_bins_all[i]
    }
  }
}

# Calculate pc percent accurately measured

for (i in 1:5) {
  # Load data
  expression_info <- read_tsv(paste0('data/expression_data/pc/abundance_by_expression_bin-pc', i, '.tsv'),
                              col_types = cols()) %>%
    mutate(min_bin_label = gsub(" .*$", "", expression_bin_label),
           pct_accurately_measured = pct_accurately_measured * 100)
  # Change sample names
  expression_info$parent_id[expression_info$parent_id == "TH_Eval_014"] <- "S1"
  expression_info$parent_id[expression_info$parent_id == "TH_Eval_015"] <- "S2"
  expression_info$parent_id[expression_info$parent_id == "TH_Eval_016"] <- "S3"
  expression_info$parent_id[expression_info$parent_id == "TH_Eval_018"] <- "S4"
  expression_info$parent_id[expression_info$parent_id == "TH_Eval_019"] <- "S5"
  # Figure out expression bin
  exp_bins <- strsplit(expression_bins_all, '-')
  for (j in 1:length(exp_bins)) {
    if ((pc_summary$measurement[i] >= as.numeric(exp_bins[[j]][1])) &&
        (pc_summary$measurement[i] < as.numeric(exp_bins[[j]][2]))) {
      expression_bin <- expression_bins_all[j]
    }
  }
  # Find average percent accurately measured
  expression_info <- expression_info %>%
    group_by(bin_median, min_bin_label) %>%
    mutate(avg_accuracy = mean(pct_accurately_measured),
           min_accuracy = min(pct_accurately_measured),
           max_accuracy = max(pct_accurately_measured))
  expression_info <- expression_info %>% ungroup()
  expression_info <- expression_info %>%
    group_by(bin_median, min_bin_label, parent_id) %>%
    mutate(avg_accuracy_sample = mean(pct_accurately_measured))
  expression_info <- expression_info %>% ungroup()
  for (j in 1:nrow(expression_info)) {
    if (expression_info$bin_median[j] == umend_depth_bin &&
        expression_info$min_bin_label[j] == expression_bin) {
      pc_summary$percent_accurate_mean[i] <- expression_info$avg_accuracy[j]
      pc_summary$percent_accurate_min[i] <- expression_info$min_accuracy[j]
      pc_summary$percent_accurate_max[i] <- expression_info$max_accuracy[j]
      if (expression_info$parent_id[j] == "S1") {
        pc_summary$percent_accurate_S1[i] <- expression_info$avg_accuracy_sample[j]
      } else if (expression_info$parent_id[j] == "S2") {
        pc_summary$percent_accurate_S2[i] <- expression_info$avg_accuracy_sample[j]
      } else if (expression_info$parent_id[j] == "S3") {
        pc_summary$percent_accurate_S3[i] <- expression_info$avg_accuracy_sample[j]
      } else if (expression_info$parent_id[j] == "S4") {
        pc_summary$percent_accurate_S4[i] <- expression_info$avg_accuracy_sample[j]
      } else if (expression_info$parent_id[j] == "S5") {
        pc_summary$percent_accurate_S5[i] <- expression_info$avg_accuracy_sample[j]
      }
    }
  }
}

# Calculate pd percent accurately measured

for (i in 1:5) {
  # Threshold 1
  if(pd_summary$pd_up1[i] == TRUE) {
   # Load data
    expression_info <- read_tsv(paste0('data/expression_data/pd/abundance_by_expression_bin-pd', i, '_1.tsv'),
                                col_types = cols()) %>%
      mutate(min_bin_label = gsub(" .*$", "", expression_bin_label),
             pct_accurately_measured = pct_accurately_measured * 100)
    # Change sample names
    expression_info$parent_id[expression_info$parent_id == "TH_Eval_014"] <- "S1"
    expression_info$parent_id[expression_info$parent_id == "TH_Eval_015"] <- "S2"
    expression_info$parent_id[expression_info$parent_id == "TH_Eval_016"] <- "S3"
    expression_info$parent_id[expression_info$parent_id == "TH_Eval_018"] <- "S4"
    expression_info$parent_id[expression_info$parent_id == "TH_Eval_019"] <- "S5"
    # Figure out expression bin
    exp_bins <- strsplit(expression_bins_all, '-')
    for (j in 1:length(exp_bins)) {
      if ((pd_summary$measurement[i] >= as.numeric(exp_bins[[j]][1])) &&
          (pd_summary$measurement[i] < as.numeric(exp_bins[[j]][2]))) {
        expression_bin <- expression_bins_all[j]
      }
    }
    # Find average percent accurately measured
    expression_info <- expression_info %>%
      group_by(bin_median, min_bin_label) %>%
      mutate(avg_accuracy = mean(pct_accurately_measured),
             min_accuracy = min(pct_accurately_measured),
             max_accuracy = max(pct_accurately_measured))
    expression_info <- expression_info %>% ungroup()
    expression_info <- expression_info %>%
      group_by(bin_median, min_bin_label, parent_id) %>%
      mutate(avg_accuracy_sample = mean(pct_accurately_measured))
    expression_info <- expression_info %>% ungroup()
    for (j in 1:nrow(expression_info)) {
      if (expression_info$bin_median[j] == umend_depth_bin &&
          expression_info$min_bin_label[j] == expression_bin) {
        pd_summary$percent_accurate_mean1[i] <- expression_info$avg_accuracy[j]
        pd_summary$percent_accurate_min1[i] <- expression_info$min_accuracy[j]
        pd_summary$percent_accurate_max1[i] <- expression_info$max_accuracy[j]
        if (expression_info$parent_id[j] == "S1") {
          pd_summary$percent_accurate1_S1[i] <- expression_info$avg_accuracy_sample[j]
        } else if (expression_info$parent_id[j] == "S2") {
          pd_summary$percent_accurate1_S2[i] <- expression_info$avg_accuracy_sample[j]
        } else if (expression_info$parent_id[j] == "S3") {
          pd_summary$percent_accurate1_S3[i] <- expression_info$avg_accuracy_sample[j]
        } else if (expression_info$parent_id[j] == "S4") {
          pd_summary$percent_accurate1_S4[i] <- expression_info$avg_accuracy_sample[j]
        } else if (expression_info$parent_id[j] == "S5") {
          pd_summary$percent_accurate1_S5[i] <- expression_info$avg_accuracy_sample[j]
        }
      }
    }
  }
  # Threshold 2
  if(pd_summary$pd_up2[i] == TRUE) {
   # Load data
    expression_info <- read_tsv(paste0('data/expression_data/pd/abundance_by_expression_bin-pd', i, '_2.tsv'),
                                col_types = cols()) %>%
      mutate(min_bin_label = gsub(" .*$", "", expression_bin_label),
             pct_accurately_measured = pct_accurately_measured * 100)
    # Change sample names
    expression_info$parent_id[expression_info$parent_id == "TH_Eval_014"] <- "S1"
    expression_info$parent_id[expression_info$parent_id == "TH_Eval_015"] <- "S2"
    expression_info$parent_id[expression_info$parent_id == "TH_Eval_016"] <- "S3"
    expression_info$parent_id[expression_info$parent_id == "TH_Eval_018"] <- "S4"
    expression_info$parent_id[expression_info$parent_id == "TH_Eval_019"] <- "S5"
    # Figure out expression bin
    exp_bins <- strsplit(expression_bins_all, '-')
    for (j in 1:length(exp_bins)) {
      if ((pd_summary$measurement[i] >= as.numeric(exp_bins[[j]][1])) &&
          (pd_summary$measurement[i] < as.numeric(exp_bins[[j]][2]))) {
        expression_bin <- expression_bins_all[j]
      }
    }
    # Find average percent accurately measured
    expression_info <- expression_info %>%
      group_by(bin_median, min_bin_label) %>%
      mutate(avg_accuracy = mean(pct_accurately_measured),
             min_accuracy = min(pct_accurately_measured),
             max_accuracy = max(pct_accurately_measured))
    expression_info <- expression_info %>% ungroup()
    expression_info <- expression_info %>%
      group_by(bin_median, min_bin_label, parent_id) %>%
      mutate(avg_accuracy_sample = mean(pct_accurately_measured))
    expression_info <- expression_info %>% ungroup()
    for (j in 1:nrow(expression_info)) {
      if (expression_info$bin_median[j] == umend_depth_bin &&
          expression_info$min_bin_label[j] == expression_bin) {
        pd_summary$percent_accurate_mean2[i] <- expression_info$avg_accuracy[j]
        pd_summary$percent_accurate_min2[i] <- expression_info$min_accuracy[j]
        pd_summary$percent_accurate_max2[i] <- expression_info$max_accuracy[j]
        if (expression_info$parent_id[j] == "S1") {
          pd_summary$percent_accurate2_S1[i] <- expression_info$avg_accuracy_sample[j]
        } else if (expression_info$parent_id[j] == "S2") {
          pd_summary$percent_accurate2_S2[i] <- expression_info$avg_accuracy_sample[j]
        } else if (expression_info$parent_id[j] == "S3") {
          pd_summary$percent_accurate2_S3[i] <- expression_info$avg_accuracy_sample[j]
        } else if (expression_info$parent_id[j] == "S4") {
          pd_summary$percent_accurate2_S4[i] <- expression_info$avg_accuracy_sample[j]
        } else if (expression_info$parent_id[j] == "S5") {
          pd_summary$percent_accurate2_S5[i] <- expression_info$avg_accuracy_sample[j]
        }
      }
    }
  }
  # Threshold 3
  if(pd_summary$pd_up3[i] == TRUE) {
   # Load data
    expression_info <- read_tsv(paste0('data/expression_data/pd/abundance_by_expression_bin-pd', i, '_3.tsv'),
                                col_types = cols()) %>%
      mutate(min_bin_label = gsub(" .*$", "", expression_bin_label),
             pct_accurately_measured = pct_accurately_measured * 100)
    # Change sample names
    expression_info$parent_id[expression_info$parent_id == "TH_Eval_014"] <- "S1"
    expression_info$parent_id[expression_info$parent_id == "TH_Eval_015"] <- "S2"
    expression_info$parent_id[expression_info$parent_id == "TH_Eval_016"] <- "S3"
    expression_info$parent_id[expression_info$parent_id == "TH_Eval_018"] <- "S4"
    expression_info$parent_id[expression_info$parent_id == "TH_Eval_019"] <- "S5"
    # Figure out expression bin
    exp_bins <- strsplit(expression_bins_all, '-')
    for (j in 1:length(exp_bins)) {
      if ((pd_summary$measurement[i] >= as.numeric(exp_bins[[j]][1])) &&
          (pd_summary$measurement[i] < as.numeric(exp_bins[[j]][2]))) {
        expression_bin <- expression_bins_all[j]
      }
    }
    # Find average percent accurately measured
    expression_info <- expression_info %>%
      group_by(bin_median, min_bin_label) %>%
      mutate(avg_accuracy = mean(pct_accurately_measured),
             min_accuracy = min(pct_accurately_measured),
             max_accuracy = max(pct_accurately_measured))
    expression_info <- expression_info %>% ungroup()
    expression_info <- expression_info %>%
      group_by(bin_median, min_bin_label, parent_id) %>%
      mutate(avg_accuracy_sample = mean(pct_accurately_measured))
    expression_info <- expression_info %>% ungroup()
    for (j in 1:nrow(expression_info)) {
      if (expression_info$bin_median[j] == umend_depth_bin &&
          expression_info$min_bin_label[j] == expression_bin) {
        pd_summary$percent_accurate_mean3[i] <- expression_info$avg_accuracy[j]
        pd_summary$percent_accurate_min3[i] <- expression_info$min_accuracy[j]
        pd_summary$percent_accurate_max3[i] <- expression_info$max_accuracy[j]
        if (expression_info$parent_id[j] == "S1") {
          pd_summary$percent_accurate3_S1[i] <- expression_info$avg_accuracy_sample[j]
        } else if (expression_info$parent_id[j] == "S2") {
          pd_summary$percent_accurate3_S2[i] <- expression_info$avg_accuracy_sample[j]
        } else if (expression_info$parent_id[j] == "S3") {
          pd_summary$percent_accurate3_S3[i] <- expression_info$avg_accuracy_sample[j]
        } else if (expression_info$parent_id[j] == "S4") {
          pd_summary$percent_accurate3_S4[i] <- expression_info$avg_accuracy_sample[j]
        } else if (expression_info$parent_id[j] == "S5") {
          pd_summary$percent_accurate3_S5[i] <- expression_info$avg_accuracy_sample[j]
        }
      }
    }
  }
  # Threshold 4
  if(pd_summary$pd_up4[i] == TRUE) {
   # Load data
    expression_info <- read_tsv(paste0('data/expression_data/pd/abundance_by_expression_bin-pd', i, '_4.tsv'),
                                col_types = cols()) %>%
      mutate(min_bin_label = gsub(" .*$", "", expression_bin_label),
             pct_accurately_measured = pct_accurately_measured * 100)
    # Change sample names
    expression_info$parent_id[expression_info$parent_id == "TH_Eval_014"] <- "S1"
    expression_info$parent_id[expression_info$parent_id == "TH_Eval_015"] <- "S2"
    expression_info$parent_id[expression_info$parent_id == "TH_Eval_016"] <- "S3"
    expression_info$parent_id[expression_info$parent_id == "TH_Eval_018"] <- "S4"
    expression_info$parent_id[expression_info$parent_id == "TH_Eval_019"] <- "S5"
    # Figure out expression bin
    exp_bins <- strsplit(expression_bins_all, '-')
    for (j in 1:length(exp_bins)) {
      if ((pd_summary$measurement[i] >= as.numeric(exp_bins[[j]][1])) &&
          (pd_summary$measurement[i] < as.numeric(exp_bins[[j]][2]))) {
        expression_bin <- expression_bins_all[j]
      }
    }
    # Find average percent accurately measured
    expression_info <- expression_info %>%
      group_by(bin_median, min_bin_label) %>%
      mutate(avg_accuracy = mean(pct_accurately_measured),
             min_accuracy = min(pct_accurately_measured),
             max_accuracy = max(pct_accurately_measured))
    expression_info <- expression_info %>% ungroup()
    expression_info <- expression_info %>%
      group_by(bin_median, min_bin_label, parent_id) %>%
      mutate(avg_accuracy_sample = mean(pct_accurately_measured))
    expression_info <- expression_info %>% ungroup()
    for (j in 1:nrow(expression_info)) {
      if (expression_info$bin_median[j] == umend_depth_bin &&
          expression_info$min_bin_label[j] == expression_bin) {
        pd_summary$percent_accurate_mean4[i] <- expression_info$avg_accuracy[j]
        pd_summary$percent_accurate_min4[i] <- expression_info$min_accuracy[j]
        pd_summary$percent_accurate_max4[i] <- expression_info$max_accuracy[j]
        if (expression_info$parent_id[j] == "S1") {
          pd_summary$percent_accurate4_S1[i] <- expression_info$avg_accuracy_sample[j]
        } else if (expression_info$parent_id[j] == "S2") {
          pd_summary$percent_accurate4_S2[i] <- expression_info$avg_accuracy_sample[j]
        } else if (expression_info$parent_id[j] == "S3") {
          pd_summary$percent_accurate4_S3[i] <- expression_info$avg_accuracy_sample[j]
        } else if (expression_info$parent_id[j] == "S4") {
          pd_summary$percent_accurate4_S4[i] <- expression_info$avg_accuracy_sample[j]
        } else if (expression_info$parent_id[j] == "S5") {
          pd_summary$percent_accurate4_S5[i] <- expression_info$avg_accuracy_sample[j]
        }
      }
    }
  }
}
  
```

### Write results

```{r}

pc_summary_dataframe <- as.data.frame(lapply(pc_summary, unlist))
pd_summary_dataframe <- as.data.frame(lapply(pd_summary, unlist))

write_tsv(pc_summary_dataframe, 'results/pc_summary.tsv')
write_tsv(pd_summary_dataframe, 'results/pd_summary.tsv')

pc_summary_dataframe_short <- pc_summary_dataframe %>%
  select(gene,
         measurement,
         outlier_threshold,
         percent_accurate_mean)

pd_summary_dataframe_short <- pd_summary_dataframe %>%
  select(gene,
         measurement,
         outlier_threshold1,
         percent_accurate_mean1,
         outlier_threshold2,
         percent_accurate_mean2,
         outlier_threshold3,
         percent_accurate_mean3,
         outlier_threshold4,
         percent_accurate_mean4)

write_tsv(pc_summary_dataframe_short, 'results/pc_summary_short.tsv')
write_tsv(pd_summary_dataframe_short, 'results/pd_summary_short.tsv')

```
